\chapter*{Acknowledgements}
\thispagestyle{empty}


Foremost, I would like to express my gratitude to Professor Debeir for his precious help during this project. I have greatly benefited from his feedback and comments. His guidance helped me during the whole process of this Master Thesis. Also, I would like to thank Professor Lenaerts and Professor Jansen for accepting to be part of my jury. Finally, I would like to thank Doctor Belgrado for letting me use his PDE camera at the César de Paepe hospital.\\

Moreover, I would like to express my deepest gratitude to my family who has always supported me during all these years of hardship. This goes especially to my mother who left her home country twenty years ago in the hope of giving her children an education and a better life. This goes without saying that she brightly succeeded in this task and all my admiration and respect goes to her. Of course, I also owe a very important debt to my brother and sister, they were trully supportive during all these years and I could not have made it without them. Finally, my deepest appreciation goes to my stepfather and his family, since my childhood they supported and helped me throughout all my university years.\\

Last but not least, a special thanks goes to my friends Maxime, Konstantin, Florian, Larby and François for making the past five years absurdly funny and ridiculous. We had our moments of despair but you all make them easier to bear. May you all succeed in the future.

\clearpage